%! Author = lavandejoey
%! Date = 21/6/2023
%! section/Abstract.tex

% Abstract
\cnabstract{
    本文从一个独特且全新的视角探索了科技与社会之间复杂而深奥的关系，通过一种富有洞察力的分析和一种无与伦比的理论框架，挑战了传统的科技决定论。
    文章在透彻地审视科技如何改变我们日常生活的基础设施和实践的同时，也关注科技如何反过来塑造社会关系和身份认知。
    这是一次对科技与社会交织关系的深入考察，将帮助读者领略到这一复杂现象的各个方面。\par
    我们通过广泛的文献回顾和深度分析，探讨了一种全新的理论框架，即“社会科技互构论”，这一框架能够全面捕捉科技与社会的相互作用和影响。
    通过将理论的力量和实践的智慧结合起来，我们开创了一种全新的理论和实践的路径，有可能引领未来科技与社会的关系研究。\par
    总的来说，这篇文章旨在打破科技与社会关系研究的旧有边界，并为未来的研究提供一个新的视角和工具。
    通过深入探讨和反思科技与社会的相互作用，我们旨在挑战现有的理论框架，并开创一种更符合现代科技社会现实的新理论。
    这不仅能促进我们对科技社会现象的理解，也能为我们处理科技与社会的复杂关系提供工具和策略。\par
}{机器学习，深度学习，神经网络，数据挖掘，自然语言处理}
\enabstract{
    This article explores the complex and esoteric relationship between technology and society from a unique and fresh perspective,
    challenging traditional technological determinism through an insightful analysis and an unparalleled theoretical framework.
    While taking a thorough look at how technology is changing the infrastructure and practices of our everyday lives,
    the article also looks at how technology is in turn shaping social relations and perceptions of identity.
    It is an in-depth examination of the intertwined relationship between technology and society
    that will help the reader to appreciate the various aspects of this complex phenomenon.\par
    Through an extensive literature review and in-depth analysis, we explore a new theoretical framework,
    'socio-technical interconstructionism', which captures the full range of interactions and impacts of technology and society.
    By combining the power of theory with the wisdom of practice, we have created a new theoretical and practical pathway that has the potential to lead the way in future research on the relationship between technology and society.\par
    Overall, this article aims to break down old boundaries in the study of the relationship between science,
    technology and society, and to provide a new perspective and tools for future research.
    By delving into and reflecting on the interactions between technology and society,
    we aim to challenge existing theoretical frameworks and pioneer a new theory that is more in line with the realities of modern technological society.
    This will not only contribute to our understanding of the social phenomenon of science and technology,
    but also provide us with tools and strategies to deal with the complex relationship between science, technology and society.\par
}{Machine Learning, Deep Learning, Neural Networks, Data Mining, Natural Language Processing}

\makeabstract